---
title: "Sales Analysis"
output: html_document
---
```{r}
install.packages("ggmap")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(lubridate)
library(ggmap)
```

Importing Sales Data from Madison Assessor's office
```{r}
sales<-read.csv("~/Documents/Berkeley/Senior Research Project/Coal Power Plants/SalesFrom2001.csv")
```

Cleaning (adding in a date column)
Assumes each sale is on the first of the month :(

```{r}
sales<-sales%>%
  filter(Sales.Price>0)%>%
  mutate(date=make_date(year=Sale.Year, month=Sale.Month))
sales
```

A quick and nonhelpful chart
```{r}
sales%>%
  filter(Sales.Price<10000000)%>%
  filter(Zip.Code%in%c(53703,53715))%>%
  ggplot()+geom_point(mapping=aes(x=date , y=Sales.Price))
```

Reading in Consumer Price Index Data
U.S. Bureau of Labor Statistics, Consumer Price Index for All Urban Consumers: All Items [CPIAUCSL], retrieved from FRED, Federal Reserve Bank of St. Louis; https://fred.stlouisfed.org/series/CPIAUCSL, October 25, 2018.
```{r}
CPI<-read.csv("CPIAUCSL.csv")
CPI
```

Converting sales to June 2018 dollars
```{r}

```

Getting Lat/long for each street address
```{r}

```

