---
title: "Sales Analysis"
output: html_document
---
```{r}

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(lubridate)
library(ggmap)
```

Importing Sales Data from Madison Assessor's office
```{r}
sales <- read_csv("~/Documents/Berkeley/Senior Research Project/Coal Plants/SalesFrom2001.csv")
sales
```

Cleaning (adding in a date column)
Assumes each sale is on the first of the month :

```{r}
cleansales<-sales%>%
  rowwise()%>%
  mutate(saleprice=as.numeric(`Sales Price`))%>%
  mutate(date=make_date(year=`Sale Year`, month=`Sale Month`))%>%
  filter(saleprice>0)%>%
  filter(saleprice<9000000)
cleansales
```
Reading in Consumer Price Index Data
U.S. Bureau of Labor Statistics, Consumer Price Index for All Urban Consumers: All Items [CPIAUCSL], retrieved from FRED, Federal Reserve Bank of St. Louis; https://fred.stlouisfed.org/series/CPIAUCSL, October 25, 2018.

Price index in September 2018 is 251.994
```{r}
CPI<-read.csv("CPIAUCSL.csv")
CPI<-CPI%>%
  rowwise()%>%
  mutate(date=as.Date(DATE))%>%
  select(CPIAUCSL, date)
```


Converting to present dollars and converting
```{r}
cleansales%>%
  filter(saleprice<1000000)%>%
  group_by(date)%>%
  summarize(median_price=median(saleprice))%>%
  left_join(CPI)%>%
  rowwise()%>%
  mutate(present_dollars=median_price*251.994/CPIAUCSL)%>%
  ggplot()+geom_point(mapping=aes(x=date , y=present_dollars))
```



Getting Lat/long for each street address
```{r}

```

